---
title: "wk2"
author: "James"
date: "2025-09-28"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r message=FALSE, warning=FALSE}
library(data.table)
library(tidyverse)
library(ggplot2)

10 + 2 # add
10 - 2 # subtract
10 * 2 # multiply
10 / 2 # divide
10 ^ 2 # exponent
10 %% 2 # modulo
13 %% 2 # modulo
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
$a+b= c$

$\text{a}+b$

a$a$

a$$a$$

# R BASIC

## ADD

a+b=c
```{r}
10+2
```
## subtract

a-b=c
```{r}
10-2
```

## multiply

a*b=c
```{r}
10*2
```

```{r}
df<-fread("https://colauttilab.github.io/RCrashCourse/FallopiaData.csv")
head(df)
glimpse(df)
df$Scenario <- as.factor(df$Scenario)
ggplot(aes(x=Total), data=df) + geom_histogram()
ggplot(aes(x=Total), data=df) + geom_density()
ggplot(aes(x=Scenario), data=df) + geom_bar()
ggplot(aes(x=Silene, y=Total), data=df) + geom_point()
ggplot(aes(x=Total), data=df) + geom_dotplot(binwidth=2)
ggplot(aes(x=Nutrients, y=Total), data=df) + geom_dotplot(binaxis="y", binwidth=2)
df %>% ggplot(aes(x=Nutrients, y=Total), data=df) +
        geom_dotplot(binaxis="y", binwidth=2)
```

download tidyverse, ggplot2, and data.table
do library and put 3 of them and run
and try add, subtract, multiply, divide, and mudulo and run it
write df<-fread and type the url
run glimpse(df)
run df$Scenario <- as.factor(df$Scenario)
and then run histogram, density, bar, and point.
last two graphs are different because their x and y of the graph are different


